Trauma treatment delay

### 2023-11-15 manuscriptlongversion.Rmd
text

The outcome is delayed treatment, as identified by the multidisciplinary
review board and recorded in the trauma care quality database.

@@

The outcome is delayed treatment, which is defined as more than 30
minutes passing from arrival before receiving treatment, as identified
by the multidisciplinary review board and recorded in the trauma care
quality database. The independent variables are gender, highest hospital
care level, GCS on arrival, respiratory rate on arrival, systolic blood
pressure on arrival, if the patient was intubated on arrival, whether
they arrived during weekend or working hours, ISS and age. Of these
variables, GCS, respiratory rate, systolic blood pressure, intubation,
ISS and age are used as continuous variables in the analysis

@@

The study size is all of the eligible patients that was treated at the
hospital between 2012 and 2022. Starting 2013 only a subgroup of
patients were screened for OFIs, but starting 2017 all patients that are
included in the database are screened for OFIs.

@@

Rstudio was used to perform the logistical regression. The code was
written to clean and prepare the data from the database. The data was
processed to have the variables customized to fit into the logistical
regression model.

@@

The 7,051 patients included in the study. 69% of the individuals
included were men, with the remaining 31% being women. The mean value
for the ISS score was 11.30, with the standard deviation being 13.22.
The majority of the patients had General care department as their
highest care level, followed by ER, ICU, OR and lastly specialized care
department. The majority of patients, 82%, were not intubated during
their stay in the hospital, followed by 9.2% intubated at the hospital
and 8.4% intubated prehospitaly. The mean age of the patients was 44.95
years old, with a standard deviation of 21.37. Most of the patients
arrived during on-call hour, 60%, with the rest arriving during working
hours. 67% of the patients arrived on a weekday, with the rest arriving
on the weekend.

@@

In the following table, the results from the regression analysis is
displayed.

@@

>>>>

The outcome is delayed treatment, as identified by the multidisciplinary
review board and recorded in the trauma care quality database. The
outcome we'll be using is "long time untill CT" and "long time until
operation", which will be referred to as delayed treatment from now on.

@@

The outcome is delayed treatment as identified by the multidisciplinary
review board and recorded in the trauma care quality database. The
independent variables are gender, highest hospital care level, GCS on
arrival, respiratory rate on arrival, systolic blood pressure on
arrival, if the patient was intubated on arrival, whether they arrived
during weekend or working hours, ISS and age. Of these variables, GCS,
respiratory rate, systolic blood pressure, intubation, ISS and age are
used as continuous variables in the analysis

@@

The study size is all of the eligible patients that was treated at the
hospital between 2012 and 2022. Starting 2013 only a subgroup of
patients were screened for OFIs, but starting 2017 all patients that are
included in the database are screened for OFIs. During this period, 69
patients were deemed to have received delayed treatment.

@@

Rstudio was used to perform the logistical regression. The code was
written to clean and prepare the data from the database. The data was
processed to have the variables customized to fit into the logistical
regression model, such as making them into factors, renaming outcomes in
the database and removing unknown values.

Using the one in ten rule, 7 independent variables were used for the
logistical regression given that we have 69 patients with delayed
treatment. The one in ten rule states that for every variable examined,
10 events are needed in the group. In this case, this means that because
we have 69 patients with the examined outcome, we can have 7 variables.
As we had more variables we wanted to use in the regression model, we
decided to run two logistical regression models. One with gender, age,
ISS, emergency procedure, SBP, RR and GCS. The other one with gender,
age, ISS, highest care level, intubation, whether they arrived during
work hours and whether they arrived on a weekday.

@@

7,051 patients included in the first logistical regression. 69% of the
individuals included were men, with the remaining 31% being women. The
mean value for the ISS score was 11.30, with the standard deviation
being 13.22. The majority of the patients had General care department as
their highest care level, followed by ER, ICU, OR and lastly specialized
care department. The majority of patients, 82%, were not intubated
during their stay in the hospital, followed by 9.2% intubated at the
hospital and 8.4% intubated prehospitaly. The mean age of the patients
was 44.95 years old, with a standard deviation of 21.37. Most of the
patients arrived during on-call hour, 60%, with the rest arriving during
working hours. 67% of the patients arrived on a weekday, with the rest
arriving on the weekend.

@@

In the following table, the results from the first regression analysis
is displayed.

@@

For the second logistical regression, we had a group size of 7,344
patients, with 70 of them having received delayed treatment. The reason
for this group having more patients is because of the exclusion criteria
that patients can't have data missing in any of the examined variables.
In this group, fewer patients had missing data, leading to fewer
exclusions. This resulted in different values in the same variables as
previously used in the first logistical regression. 68% of the
individuals included were men, with the remaining 32% being women. The
mean value for the ISS score was 10.07, with the standard deviation
being 10.27. The mean age of the patients was 44.20 years old, with a
standard deviation of 21.41. The majority of the patients had no
emergency measures performed, with 76% of the patients belonging to this
group. Following this, the most common emergency procedures were other
action, laparotomy, craniotomy, radiological intervention, intracranial
pressure measurement, and lastly, revascularization. The mean SBP was
137.60, with a standard deviation of 25.09. Mean respiratory rate was
18.59 with a standard deviation of 5.10. Lastly, mean GCS was 13.95,
with a standard deviation of 2.58.

![](table2.png)

In the following table, the results from the second regression analysis
is displayed.

The odds ratio is calculated in the same way as the previous regression
model, as well as a 95% confidence interval. The p value is also shown.

![](results2.png)
